\documentstyle[11pt]{article}
\setlength{\parindent}{0em}
\begin{document}
\begin{center}
{\LARGE \begin{bf}CSE 341\end{bf}: Compilers and Interpreters \\  }
Project Submission \\
Mike Berry (\begin{it}berrym@seas.upenn.edu\end{it}) \\

\end{center}

\section{High level description}

The project consists of a compiler (\begin{it}``mcc''\end{it}) that
compiles a subset of the C language into SPARC Assembly language. \\

The compiler consist of three distinct phases:
\begin{enumerate}

\item lexical analysis

\item parsing

\item code generation
\end{enumerate}

Type checking and symbol management are done throughout the three
stages.

\section{The source code}

\subsection{Management}

The source code is managed by \begin{it}RCS\end{it} and compiled using the
\begin{it}make\end{it} utility.

The source code is divided up somewhat along the lines of the
major functions described in section 1:

\begin{itemize}

\item globals.h -- structures, global variabes, and function prototypes

\item mcc.l -- flex lexer

\item mcc.y -- bison parser

\item symbol.c -- symbol table management

\item tree.c -- syntax tree management, type checking

\item register.c -- code generation, register allocation
\end{itemize}

\subsection{Compiling}

Using the make utility, the code compiles into an executable called mcc.

\begin{verbatim}
$ make 
bison -v -d mcc.y
gcc -g  symbol.c -c
gcc -g  tree.c -c
/usr/local/bin/flex mcc.l
gcc -g  lex.yy.c -c
gcc -g  mcc.tab.c -c
gcc -g  register.c -c
gcc -g  -o mcc symbol.o lex.yy.o mcc.tab.o tree.o register.o -lfl -ly
\end{verbatim}

\section{What works; what doesn't work}

The primary weakness of \begin{it}mcc\end{it} is inefficient code
generation.  Registers are flushed and loaded to and from the
stack often; global registers are not used at all; local registers are not
used often enough. \\


Also, global variables were not implemented correctly and dropped.  I 
have also noticed that integer $\rightarrow$ float raising does
not occur in some instances; however, it does occur correctly in
all the sample programs.  I was unable to isolate the source
of the problem.

\section{Submission}

There are three ``useful'' programs which demonstrate
commonly known non-trvial algorithms, and one ``useless'' program
which demonstrates various control structures and expressions. \\


With each program is the mcc source, assembly output from mcc,
and compile/ runtime shell logs.

\begin{enumerate}

\item fquick -- quick sort

\item ssort -- shell sort

\item factorial -- factorial 

\item sample -- ``useless''


\end{enumerate}
Also attached is the full source listing.

\section{Acknowledgements}

I'd like to thank my roommates for putting up with me talking
to myself while wearing a bicycle helmet while doing this project.

\end{document}

